\ab{Constraints on quasi--normal-mode frequencies with LIGO-Virgo binary--black-hole observations}

### 2021-03-17 papers/intro_paper/results_lvc.tex
changes up to Sec. IV

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Table for LVC values
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}
\input{table_lvc_results}
\caption{The median, and symmetric 90\% credible intervals of the frequency and damping time of the $(2,\pm2)$ QNM, and the mass and spin of the remnant object estimated from the measurements of the QNM frequencies.}
\label{tab:qnm_o1o2_results}
\end{table}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Table for LVC values
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}
\input{table_lvc_results}
\caption{The median and symmetric 90\% credible intervals of the frequency and damping time of the $(2,\pm2)$ QNM, and the mass and spin of the remnant object estimated from 
the QNM frequencies \ab{using the $\pSEOB$ model.} \comment{AB: I would add the mass and spin of the remnant from NR fits, as well. The final mass should be multiplied by $(1+z)$. Correct?}}
\label{tab:qnm_o1o2_results}
\end{table}
